### 2020-11-22 latex/acrobot.tex
Completed oscillation energy proof
Also completed first edit of perturbation section for oscillations. Needs one more pass
before sending to Manfredi.

\begin{figure}
    \centering
    \includestandalone[width=0.7\textwidth]{images/simple_acrobot_model}
    \caption{A simple acrobot has massless rods of equal length \(l\) and 
    equal masses \(m\) at the tips.}
    \label{fig:simple-acrobot-model}
\end{figure}

@@

\begin{prop}\label{prop:acrobot-fpu-regular}
    A relation \(h(q,p) = q_a - f(p_u) = 0\) for ~\eqref{eqn:acrobot-hamiltonian} 
    with \(f \in C^2\left(\mathcal{P}_u; \mathcal{Q}_a\right)\) is a regular
    VNHC of order 1.
\end{prop}
\begin{proof}
    Since \(\partial_{q_u} f = 0\), the regularity equation
    ~\eqref{eqn:regularity-matrix-acrobot} is strictly positive for all values
    of \(q_a\), and hence is full rank everywhere on the constraint manifold.
    By Theorem \ref{thm:vnhc-regularity}, \(h\) is a regular VNHC of order 1.
\end{proof}
Proposition \ref{prop:acrobot-fpu-regular} will be useful later, as we will not
need to check regularity if we design a function of the unactuated momentum.

@@

\section{Previous Constraint Approaches}
% TODO: Give Xingbo's intuition, abstract away to qa = sin(theta) constraint
% based on VLP but show it doesn't work well in our framework
% TODO: Describe Xingbo's results and observe that his results were similar to a VNHC
% except they used VHC tools. We will modify his approach to use VNHCs and prove
% rigorously that we can stabilize any energy level set on the acrobot.
Let us examine some of the existing approaches to generating giant motion for
the acrobot, since these may be viable candidates on which to base a VNHC.

@@

\section{The Acrobot Constraint}
% TODO: Give the constraint, state the theorem, and show the outline of the
% proof (both as a sketch and in a figure)
One may be tempted to design a constraint of the form \(q_a = \bar{q}_a\sin(\theta)\) 
with \(\theta := \arctan_2(p_u,q_u)\), since a similar approach 
was so effective for the VLP in Chapter \ref{ch:vlp}.
Unfortunately, this constraint is not regular, and it is difficult to find any
VNHC of the form \(q_a = f(\theta)\) where regularity can be proven easily.
Instead, we will develop a constraint \(h(q,p) = q_a - f(p_u)\) because these
constraints are always regular (as per Proposition \ref{prop:acrobot-fpu-regular}).

@@

The acrobot's legs are rigid rods which cannot retract, so we emulate the person
on a swing by pivoting the legs toward the direction of motion. 
To account for how a person leans back at higher speeds, the legs should pivot to an
angle proportional to the swing's speed.
Since the direction of motion is entirely determined by \(p_u\), 
one such VNHC which emulates this process is \(q_a = \bar{q}_a\arctan( I p_u)\),
displayed in Figure \ref{fig:qa-arctan}.
Here, \(\bar{q}_a \in ]0,\frac{2 Q_a}{\pi}]\) and \(I \in \R_{>0}\) is a fixed
control parameter.

This constraint does not perfectly recreate giant motion, during which
the gymnast's legs are almost completely extended -- it instead pivots the legs
partially during rotations.
However, the behaviour looks similar enough that the constraint should provide a
decent foundation for injecting energy into the acrobot.
It is for this reason that we choose our acrobot's constraint to be
\begin{equation}\label{eqn:acrobot-constraint}
    h(q,p) = q_a - \bar{q}_a \arctan(I p_u)
    .
\end{equation}

@@

\section{Proving the Acrobot Gains Energy}\label{sec:acrobot-proof}
% TODO: Prove this in sections
% TODO: You don't have to use the proof of theta_dot being positive. Stick to
% Manfredi's proof, and when you say "for I small enough" put in a footnote that
% says "in fact, we can be more precise and set bounds for I given as I <
% min{...}. See appendix for more detail."
% Then, we can have an appendix where we derive the bounds on I so that
% theta_dot is always positive. This will help the reader keep track and not
% bother them too much.
Proving Theorem \ref{thm:acrobot-energy-stabilization} is not a simple task.
In an effort to make the proof as clear as possible, we will break it down into
the following segments:
\begin{enumerate}
    \item Background on perturbation theory.
    \item Perturbation analysis for oscillations.
    \item Energy gain for oscillations.
    \item Perturbation analysis for rotations.
    \item Energy gain for rotations.
\end{enumerate}

@@

\subsection*{Background on Perturbation Theory}
Nonlinear systems like the acrobot are difficult (or impossible) to solve
analytically.
Perturbation theory allows one to understand the behaviour of the nonlinear system
by studying a simpler nominal system. 
Solutions of the nonlinear system can often be approximated by taking a Taylor
expansion around this nominal system.

\citet{khalil_nonlinear} considers a system of the form

\begin{equation}\label{eqn:khalil-setup}
    \begin{cases}
        \dot{x} = f(t,x,I), \\
        x(t_0) = \eta(I),
    \end{cases}
\end{equation}
where 
\(f : [t_0,t_1] \times D \times [-I_0,I_0] \rightarrow \R^n\) is smooth 
\footnote{Khalil actually considers \(f(t,x,\epsilon)\) which is ``sufficiently
    smooth". We replace \(\epsilon\) with \(I\) and assume smoothness to
    more easily connect his theory to the acrobot constraint.}
on a domain \(D \subset \R^n\).
In the context of the acrobot, \(x\) is the any coordinates which make
our analysis convenient;
\(I\) is a control parameter of the system;
the function \(f\) is the constrained dynamics in \(x\)-coordinates;
and \(\eta(I) \equiv \eta_0\) is a constant initial condition.

Setting \(I = 0\) we get the nominal system
\begin{equation}\label{eqn:khalil-perturbation-nominal}
    \begin{cases}
        \dot{x}_0 = f(t,x,0) ,\\
        x_0(t_0) = \eta_0 ,
    \end{cases}
\end{equation}
which we need to solve for the explicit solution \(x_0(t,\eta_0)\) on \([t_0,t_1]\).
One can use this to compute the solution \(x_1(t,\eta_0)\) of
\begin{equation}\label{eqn:khalil-perturbation-firstorder}
    \begin{cases}
        \dot{x}_1 = \pdiff{f}{x}(t,x_0(t,\eta_0),0)x_1 + \pdiff{f}{I}(t,x_0(t,\eta_0),0)
        , \\
        x_1(t_0,\eta_0) = 0
        .
    \end{cases}
\end{equation}
Finally, one can compute the first-order Taylor approximation
\(x(t,\eta_0,I) = x_0(t,\eta_0) + I x_1(t,\eta_0) + R(t,\eta_0,I)\), where the remainder
term \(R(t,\eta_0,I)\) is smooth and \(O(I^2)\), \ie,
\[
    \lim \limits_{I \to 0} \frac{R(t,I)}{I} = 0
    .
\]
We now paraphrase Khalil's Theorem 10.1 \cite{khalil_nonlinear} on the
accuracy of perturbation analysis.
\begin{thm}\label{thm:khalil-perturbation}
    Suppose \(f : [t_0,t_1] \times D \times [-I_0,I_0] \rightarrow \R^2\) is
    \(C^1\), and that the nominal problem ~\eqref{eqn:khalil-perturbation-nominal} has a
    unique solution \(x_0(t,\eta_0) \in D\) on \([t_0,t_1]\).
    Then there exists \(I^\star > 0\) such that, for all \(I\) with \(|I| < I^\star\), the
    solution \(x(t,\eta_0,I)\) to ~\eqref{eqn:khalil-setup} satisfies
    \[
        \norm{x(t,\eta_0,I) - \left(x_0(t,\eta_0) + I x_1(t,\eta_0)\right)} \leq k |I^2|
    \]
    for some \(k > 0\).
\end{thm}

@@

\subsection*{Perturbation Analysis for Oscillations}
As we have seen, setting \(I = 0\) turns the acrobot into a nominal pendulum. 
This pendulum oscillates whenever the nominal energy
~\eqref{eqn:acrobot-nominal-E} is less than \(E(\pi,0)\). 
Hence, the domain of oscillations for the nominal pendulum is given by
\[
    \mathcal{O} := \left\{ (q_u,p_u) \in \Gamma \mid E(q_u,p_u) < E(\pi,0)\right\}
    ,
\]
where \(\Gamma \simeq \SxR\) is the constraint manifold of the
acrobot.
Recall that orbits of a pendulum are level sets of \(E\). 
From Figure \ref{fig:pendulum-level-sets}, we know oscillations of a pendulum
look like ellipses contained in \(\mathcal{O}\).
Since perturbation theory requires us to analyze the nominal pendulum, we will
make our analysis convenient by changing coordinates into a
``radius" \(\mu > 0\) which remains constant on level sets of \(E\), 
along with an ``angle" \(\alpha \in \Sone\) satisfying \(\dot{\alpha} > 0\) on
\(\mathcal{O}\).

@@

Suppose at time \(t = 0\) we have initialized the acrobot at \((\alpha,\mu) = (0,\mu_0)\).
Since \(\alpha\) is continuously increasing, we know that the orbit will do one
of two things: it will either leave \(\mathcal{O}\) so that the acrobot is now rotating,
or it will remain in \(\mathcal{O}\) and hit the \(q_u\)-axis at some point 
\((\alpha,\mu) = (\pi,m)\).
From there, the acrobot could escape \(\mathcal{O}\) along the second half of the orbit or
return to some point \((\alpha,\mu) = (0,\tilde{m})\) (as illustrated in Figure
\ref{fig:acrobot-possible-orbits}).
If \(\tilde{m} < \mu_0\) then the acrobot has lost energy; 
if \(\tilde{m} = \mu_0\), the acrobot is on a closed orbit;
and if \(\tilde{m} > \mu_0\) the acrobot has gained energy.
Which situation occurs might depend entirely on the choice of
\(\mu_0\).

\begin{figure}
    \centering 
    % TODO: Draw the domain mathcalO, an initial point (q0,p0) = (mu0,0), and show the
    % half orbit hitting the left q-axis at (-m,0).
    % Then show the 
    % 4 clockwise half orbits starting at (-m,0): 
    % one orbit exits mathcalO on the top right corner;
    % one orbit hits the right q-axis at (mu0+x,0); 
    % one hits (mu0,0);
    % and one hits (mu0-x,0) for some x > 0.
    %includestandalone[width=0.5\textwdith]{images/acrobot_possible_orbits}
    \caption{If the acrobot is initialized at \((q_u,p_u) = (\mu_0,0)\), then
        either the orbit escapes \(\mathcal{O}\) into the rotation
        zone (purple), or the orbit hits the other half of the \(q_u\)-axis 
        with a higher (red), equal (black), or lower (blue) angle than when it
        started.}
    \label{fig:acrobot-possible-orbits}
\end{figure}

We can simplify the analysis of where orbits intersect the \(q_u\)-axis 
by studying how the system behaves on average.
Since \(\dot{\alpha} > 0\), we could theoretically find some time scaling 
\(t = \tau(\alpha)\) and use \(\alpha\) as a new ``time" variable.
Setting \(\hat{\mu}(\alpha) := \mu(\tau(\alpha))\) allows us to ignore the
dynamics of \(\alpha\) (assuming the acrobot remains in \(\mathcal{O}\)).
This allows us to study the evolution of \(\mu\) as a 
function of \(\alpha\) rather than as a function of time.
The dynamics of \(\hat{\mu}\) are
\[
    \diff{\hat{\mu}}{\alpha} = 
    \left.\diff{\mu}{t} \diff{t}{\alpha} \right|_{t =\tau(\alpha)}
    ,
\] 
yielding the ``time"-varying scalar ODE
\begin{equation}\label{eqn:muhat-dot}
    \begin{cases}
        \diff{\hat{\mu}}{\alpha} 
        = \frac{f_\mu(\tau(\alpha),\mu,I)}{f_\alpha(\tau(\alpha),\mu,I)}
        =: g(\alpha,\mu,I)
        , \\
        \hat{\mu}(0) = \mu_0
        .
    \end{cases}
\end{equation}
with solution \(\hat{\mu}(\alpha,\mu_0,I)\).

@@

Likewise, ~\eqref{eqn:khalil-perturbation-firstorder} tells us that 
\(\hat{\mu}_1\) is the solution to
\begin{equation}\label{eqn:acrobot-mu1-dot}
    \begin{cases}
        \dot{\hat{\mu}}_1 = a(\alpha,\mu_0)\hat{\mu}_1 + b(\alpha,\mu_0)
        , \\
        \hat{\mu}_1(0) = 0
        .
    \end{cases}
\end{equation}
where
\begin{align*}
    a(\alpha,\mu_0) &= \pdiff{g}{\hat{\mu}}(\alpha,\mu_0,0)
    , \\
    b(\alpha, \mu_0) &= \pdiff{g}{I}(\alpha, \mu_0, 0)
    .
\end{align*}
These are difficult to compute by hand, so we resort to MATLAB symbolic
computation to reveal that
\begin{align*}
    a(\alpha,\mu_0) &= 0
    , \\
    b(\alpha,\mu_0) &= K \hat{b}(\alpha,\mu_0)
    ,
\end{align*}
where we define
\begin{align*}
    K &:= \frac{\bar{q}_a \sqrt{30m^2g l^3}}{15}
    , \\
    \hat{b}(\alpha,\mu_0) &:= \frac{
        \mu_0 |\sin(\alpha)| \left(
        5 c_{\mu_0} \cos(\mu_0 c_\alpha) - 8 \cos(\mu_0c_\alpha)^2 + 3
    \right)
    }{
    \sin(\mu_0)\sqrt{\cos(\mu_0c_\alpha) - c_{\mu_0}}
    }
    .
\end{align*}
Hence, the solution to ~\eqref{eqn:acrobot-mu1-dot} is given by
\[
    \hat{\mu}_1(\alpha,\mu_0) =
    K \int \limits_0^\alpha \hat{b}(\sigma,\mu_0)d\sigma
    .
\]

Suppose we initialize the acrobot at \((\alpha,\mu) = (0,\mu_0)\). 
After half an oscillation, when \(\alpha = \pi\), the orbit will land on the
negative \(q_u\)-axis with pseudo-radius 
\(m = \hat{\mu}(\pi,\mu_0) \approx \mu_0 + I\hat{\mu}_1(\pi,\mu_0)\).
Hence, the change in pseudo-radius is 
\(m - \mu_0 \approx I\hat{\mu}_1(\pi,\mu_0)\).
If the orbit remains in \(\mathcal{O}\) for the full oscillation, 
it will land on the positive \(q_u\)-axis
with pseudo-radius
\(\tilde{m} \approx \mu_0 + I\hat{\mu}_1(2\pi,\mu_0)\).

Notice that \(\hat{b}(\alpha,\mu_0)\) is even and 
\(\pi\)-periodic in \(\alpha\), so that
\begin{equation}\label{eqn:bhat-integral-properties}
    \int \limits_{-\pi}^\pi \hat{b}(\sigma,\mu_0) d\sigma
    = \int \limits_0 ^ {2 \pi} \hat{b}(\sigma,\mu_0) d\sigma
    = 2 \int \limits_0^\pi \hat{b}(\sigma,\mu_0) d\sigma
    .
\end{equation}
This implies that 
\(\hat{\mu}_1(2\pi,\mu_0) = 2 \hat{\mu}_1(\pi,\mu_0)\),
which means the change in pseudo-radius after a full oscillation is 
\(\tilde{m} - \mu_0 \approx 2I\hat{\mu}_1(\pi,\mu_0)\).
If \(\hat{\mu}_1(\pi,\mu_0) > 0\), 
then both \(m - \mu_0 > 0\) and \(\tilde{m} - \mu_0 > 0\).
In other words, we can study the average behaviour of \(\hat{\mu}\) by examining
the behaviour over each half oscillation.

We define the Poincar\'{e} section 
\(P_\mathcal{O}(\mu_0) := \hat{\mu}(\pi,\mu_0)\)
corresponding to the change in \(\hat{\mu}\) after half an oscillation.
The section expands into
\[
    P_\mathcal{O}(\mu_0) = \mu_0 + I \hat{\mu}_1(\pi,\mu_0) + R(\pi,\mu_0,I)
    .
\]
Let us define
\[
    Q(\mu_0) := \int \limits_0^\pi \hat{b}(\sigma,\mu_0)d\sigma
    ,
\]
so that \(\hat{\mu}_1(\pi,\mu_0) = K Q(\mu_0)\).
Note that \(K\) is a positive constant which contains the acrobot's physical
parameters, while \(\hat{b}(\alpha,\mu)\) is adimensional. 
This means \(Q(\mu_0)\) is identical for every acrobot.
If \(Q(\mu_0)\) is strictly positive, then \(\hat{\mu}_1(\pi,\mu_0)\) will be
positive no matter the values of \(m\), \(g\), \(l\), or \(\bar{q}_a\).

@@

Let \(x(0) \in \mathcal{O}_\epsilon \subset \mathcal{O}\).
Since \(\dot{\alpha} > 0\), the orbit \(x(t)\) spirals clockwise around
the origin.
If this orbit remains in \(\mathcal{O}\), it must intersect
the \(q_u\) axis at some radius \(\mu = \delta\)
which depends on the initial condition \(x(0)\).
Take 
\[
    \underbar{\delta} = 
    \min\limits_{x(0) \in \bar{\mathcal{O}}_\epsilon} \delta(x(0))
    ,
\] 
which exists because \(\bar{\mathcal{O}}_\epsilon\) is compact.
From the previous perturbation analysis,
there exists \(I\) small enough that \(P_\mathcal{O}(\mu_0)\) 
is positive for all \(\mu_0 \in [\underbar{\delta},\pi[\).

Suppose \(x(0) \in \mathcal{O}_\epsilon\), and the orbit
intersects the \(q_u\)-axis at some point \(x(t_0) = (m_0, 0)\).
The Poincar\'{e} section \(P_\mathcal{O}(|m_0|)\) is positive because 
\(|m_0| \geq \underbar{\delta}\).
As the acrobot continues its oscillation, it will intersect the \(q_u\) axis
again at a new point \(x(t_1) = (m_1,0)\).

Setting \(p_1 := P_\mathcal{O}(|m_0|)\),
Theorem \ref{thm:khalil-perturbation} guarantees that
\[
    \norm{m_1 - p_1} \leq cI^2
    ,
\]
for some \(c > 0\).
%TODO 
\textbf{SHOW THIS IMPLIES |m1| > |m0|}

From here, we can apply Theorem \ref{thm:khalil-perturbation} iteratively:
initializing the acrobot at \(x(t_i) = (m_i, 0)\), the
next intersection with the \(q_u\) axis will be at
\(x(t_{i+1}) = (m_{i+1},0)\) with \(|m_{i+1}| > |m_i|\).

>>>>

\begin{figure}
    \centering
    \includestandalone[width=0.5\textwidth]{images/simple_acrobot_model}
    \caption{A simple acrobot has massless rods of equal length \(l\) and 
    equal masses \(m\) at the tips.}
    \label{fig:simple-acrobot-model}
\end{figure}

@@

\begin{prop}\label{prop:acrobot-fpu-regular}
    A relation \(h(q,p) = q_a - f(p_u) = 0\) 
    with \(f \in C^2\left(\mathcal{P}_u; \mathcal{Q}_a\right)\) is a regular
    VNHC of order 1 for the simple acrobot.
\end{prop}
\begin{proof}
    Since \(\partial_{q_u} f = 0\), the regularity equation
    ~\eqref{eqn:regularity-matrix-acrobot} is strictly positive for all values
    of \(q_a\), and hence is full rank everywhere on the constraint manifold.
    By Theorem \ref{thm:vnhc-regularity}, \(h\) is a regular VNHC of order 1.
\end{proof}
Proposition \ref{prop:acrobot-fpu-regular} will be useful later, as we will not
need to check regularity if we design a function of the unactuated momentum.

@@

\section{Previous Constraint Approaches}
Let us examine some of the existing approaches to generating giant motion for
the acrobot, since these may be viable candidates on which to base a VNHC.

@@

\section{The Acrobot Constraint}
One may be tempted to design a constraint of the form \(q_a = \bar{q}_a\sin(\theta)\) 
with \(\theta := \arctan_2(p_u,q_u)\), since a similar approach 
was so effective for the VLP in Chapter \ref{ch:vlp}.
Unfortunately, this constraint is not regular, and it is difficult to find any
VNHC of the form \(q_a = f(\theta)\) where regularity can be proven easily.
Instead, we will develop a constraint \(h(q,p) = q_a - f(p_u)\) because these
constraints are always regular (as per Proposition \ref{prop:acrobot-fpu-regular}).

@@

The acrobot's legs are rigid rods which cannot retract, so we emulate the person
on a swing by pivoting the legs toward the direction of motion. 
To account for how a person leans back at higher speeds, the legs should pivot to an
angle proportional to the swing's speed.
Since the direction of motion is entirely determined by \(p_u\), 
one such VNHC which emulates this process is \(q_a = \bar{q}_a\arctan( I p_u)\),
displayed in Figure \ref{fig:qa-arctan}.
Here, \(\bar{q}_a \in ]0,\frac{2 Q_a}{\pi}]\) and \(I \in \R\) is a fixed
control parameter.

This constraint does not perfectly recreate giant motion, during which
the gymnast's legs are almost completely extended \cite{usagym_giant}
-- it instead pivots the legs partially during rotations.
However, the behaviour looks similar enough that the constraint should provide a
decent foundation for injecting energy into the acrobot.
It is for this reason that we choose our acrobot's constraint to be
\begin{equation}\label{eqn:acrobot-constraint}
    h(q,p) = q_a - \bar{q}_a \arctan(I p_u)
    .
\end{equation}

@@

\section{Proving the Acrobot Gains Energy}\label{sec:acrobot-proof}
Proving Theorem \ref{thm:acrobot-energy-stabilization} is not a simple task.
In an effort to make the proof as clear as possible, we will break it down into
the following segments:
\begin{enumerate}
    \item Background on perturbation theory.
    \item Perturbation analysis for oscillations.
    \item Energy gain for oscillations.
    \item Perturbation analysis for rotations.
    \item Energy gain for rotations.
\end{enumerate}

@@

\subsection*{Background on Perturbation Theory}
Nonlinear systems like the acrobot are difficult (or even impossible) to solve
analytically.
Perturbation theory allows one to understand the behaviour of nonlinear systems
by studying a simpler nominal system. 
Solutions of the nonlinear system can often be approximated by taking a Taylor
expansion around this nominal system.

\citet{khalil_nonlinear} considers a system of the form
\begin{equation}\label{eqn:khalil-setup}
    \begin{cases}
        \dot{x} = f(t,x,I), \\
        x(t_0) = \eta(I),
    \end{cases}
\end{equation}
where 
\(f : [t_0,t_1] \times D \times [-I_0,I_0] \rightarrow \R^n\) is  
smooth\footnote{Khalil actually considers \(f(t,x,\epsilon)\) which is ``sufficiently
    smooth". To more easily connect his theory to the acrobot constraint, we
    assume smoothness of \(f\) and replace \(\epsilon\) with \(I\).}
on a domain \(D \subset \R^n\).
In the context of the acrobot, \(x\) is any pair of coordinates which make
our analysis convenient;
\(I\) is the control parameter of the system;
the function \(f\) is the constrained dynamics in \(x\)-coordinates;
and \(\eta(I) \equiv \eta_0\) is a constant initial condition.

Setting \(I = 0\) we get the nominal system
\begin{equation}\label{eqn:khalil-perturbation-nominal}
    \begin{cases}
        \dot{x}_0 = f(t,x,0) ,\\
        x_0(t_0) = \eta_0 ,
    \end{cases}
\end{equation}
which we need to solve for the explicit solution \(x_0(t,\eta_0)\) on \([t_0,t_1]\).
One can use this to compute the solution \(x_1(t,\eta_0)\) of
\begin{equation}\label{eqn:khalil-perturbation-firstorder}
    \begin{cases}
        \dot{x}_1 = \pdiff{f}{x}(t,x_0(t,\eta_0),0)x_1 + \pdiff{f}{I}(t,x_0(t,\eta_0),0)
        , \\
        x_1(t_0,\eta_0) = 0
        .
    \end{cases}
\end{equation}
Finally, one can compute the first-order Taylor approximation 
\(x(t,\eta_0,I) = x_0(t,\eta_0) + I x_1(t,\eta_0) + R(t,\eta_0,I)\), where the remainder
term \(R(t,\eta_0,I)\) is smooth and \(O(I^2)\), \ie,
\[
    \lim \limits_{I \to 0} \frac{R(t,I)}{I} = 0
    .
\]
We now paraphrase Khalil's Theorem 10.1 \cite{khalil_nonlinear} on the
accuracy of perturbation analysis.
\begin{thm}\label{thm:khalil-perturbation}
    Suppose \(f : [t_0,t_1] \times D \times [-I_0,I_0] \rightarrow \R^2\) is
    \(C^1\), and that the nominal system ~\eqref{eqn:khalil-perturbation-nominal} has a
    unique solution \(x_0(t,\eta_0) \in D\) on \([t_0,t_1]\).
    Then there exists \(I^\star > 0\) such that, for all \(I\) with \(|I| < I^\star\), the
    solution \(x(t,\eta_0,I)\) to ~\eqref{eqn:khalil-setup} satisfies
    \[
        \norm{x(t,\eta_0,I) - \left(x_0(t,\eta_0) + I x_1(t,\eta_0)\right)} \leq k |I^2|
    \]
    for some \(k > 0\).
\end{thm}

@@

\subsection*{Perturbation Analysis for Oscillations}
As we have seen, setting \(I = 0\) turns the acrobot into a nominal pendulum. 
This pendulum oscillates whenever the nominal energy
~\eqref{eqn:acrobot-nominal-E} is less than \(E(\pi,0)\). 
Hence, the domain of oscillations for the nominal pendulum is given by
\[
    \mathcal{O} := \left\{ (q_u,p_u) \in \Gamma \mid E(q_u,p_u) < E(\pi,0)\right\}
    ,
\]
where \(\Gamma \simeq \SxR\) is the constraint manifold of the
acrobot.
Recall that orbits of a pendulum are level sets of \(E\). 
From Figure \ref{fig:pendulum-level-sets}, we know that oscillation level sets
look like ellipses contained in \(\mathcal{O}\).
Since perturbation theory requires us to analyze the nominal pendulum, we will
make our analysis convenient by changing coordinates into a
``radius" \(\mu > 0\) which remains constant on level sets of \(E\), 
along with an ``angle" \(\alpha \in \Sone\) satisfying \(\dot{\alpha} > 0\) on
\(\mathcal{O}\).

@@

Suppose at time \(t = 0\) we have initialized the acrobot at \((\alpha,\mu) = (0,\mu_0)\).
Since \(\alpha\) is continuously increasing, we know that the orbit will do one
of two things: it will either leave \(\mathcal{O}\) so that the acrobot is now rotating,
or it will remain in \(\mathcal{O}\) and hit the \(q_u\)-axis at some point 
\((\alpha,\mu) = (\pi,u)\).
From there, the acrobot could escape \(\mathcal{O}\) along the second half of the orbit or
return to some point \((\alpha,\mu) = (0,\tilde{u})\) (as illustrated in Figure
\ref{fig:acrobot-possible-orbits}).
If \(\tilde{u} < \mu_0\) then the acrobot has lost energy; 
if \(\tilde{u} = \mu_0\), the acrobot is on a closed orbit;
and if \(\tilde{u} > \mu_0\) the acrobot has gained energy.
Which situation occurs might depend entirely on the choice of
\(\mu_0\).

\begin{figure}
    \centering 
    % TODO: Draw the domain mathcalO, an initial point (q0,p0) = (mu0,0), and show the
    % half orbit hitting the left q-axis at (-m,0).
    % Then show the 
    % 4 clockwise half orbits starting at (-m,0): 
    % one orbit exits mathcalO on the top right corner;
    % one orbit hits the right q-axis at (mu0+x,0); 
    % one hits (mu0,0);
    % and one hits (mu0-x,0) for some x > 0.
    %includestandalone[width=0.5\textwdith]{images/acrobot_possible_orbits}
    \caption{If the acrobot is initialized at \((q_u,p_u) = (\mu_0,0)\), then
        either the orbit escapes \(\mathcal{O}\) into the rotation
        zone (purple), or the orbit returns to the \(q_u\)-axis 
        with a higher (red), equal (black), or lower (blue) pseudo-radius than when it
        started.}
    \label{fig:acrobot-possible-orbits}
\end{figure}

We can simplify our analysis of the acrobot by studying how its orbits
intersect the \(q_u\)-axis on average.
Since \(\dot{\alpha} > 0\), we could theoretically find some time scaling 
\(t = \tau(\alpha)\) and use \(\alpha\) as a new ``time" variable.
Setting \(\hat{\mu}(\alpha) := \mu(\tau(\alpha))\) allows us to ignore the
dynamics of \(\alpha\) by observing the evolution of \(\mu\) as a function of
\(\alpha\) rather than a function of time (assuming the acrobot remains in
\(\mathcal{O}\)).
The dynamics of \(\hat{\mu}\) are
\[
    \diff{\hat{\mu}}{\alpha} = 
    \left.\diff{\mu}{t} \diff{t}{\alpha} \right|_{t =\tau(\alpha)}
    ,
\] 
yielding the ``time"-varying scalar ODE
\begin{equation}\label{eqn:muhat-dot}
    \begin{cases}
        \diff{\hat{\mu}}{\alpha} 
        = \frac{f_\mu(\tau(\alpha),\mu,I)}{f_\alpha(\tau(\alpha),\mu,I)}
        =: g(\alpha,\mu,I)
        , \\
        \hat{\mu}(0) = \mu_0
        .
    \end{cases}
\end{equation}

@@

Likewise, ~\eqref{eqn:khalil-perturbation-firstorder} tells us that 
\(\hat{\mu}_1\) is the solution to
\begin{equation}\label{eqn:acrobot-mu1-dot}
    \begin{cases}
        \dot{\hat{\mu}}_1 = 
        \pdiff{g}{\hat{\mu}}(\alpha,\mu_0,0)\hat{\mu}_1 + \pdiff{g}{I}(\alpha, \mu_0, 0)
        , \\
        \hat{\mu}_1(0) = 0
        .
    \end{cases}
\end{equation}
These dynamics are difficult to compute by hand, so we resort to MATLAB symbolic
computation to reveal that
\begin{align*}
    \pdiff{g}{\hat{\mu}}(\alpha,\mu_0,0) &= 0
    , \\
    \pdiff{g}{I}(\alpha, \mu_0, 0) &= K b(\alpha,\mu_0)
    ,
\end{align*}
where we define
\begin{align*}
    K &:= \frac{\bar{q}_a \sqrt{30m^2g l^3}}{15}
    , \\
    b(\alpha,\mu_0) &:= \frac{
        \mu_0 |\sin(\alpha)| \left(
        5 c_{\mu_0} \cos(\mu_0 c_\alpha) - 8 \cos(\mu_0c_\alpha)^2 + 3
    \right)
    }{
    \sin(\mu_0)\sqrt{\cos(\mu_0c_\alpha) - c_{\mu_0}}
    }
    .
\end{align*}
Hence, the solution to ~\eqref{eqn:acrobot-mu1-dot} is given by
\[
    \hat{\mu}_1(\alpha,\mu_0) =
    K \int \limits_0^\alpha b(\sigma,\mu_0)d\sigma
    .
\]

Suppose we initialize the acrobot at \((\alpha,\mu) = (0,\mu_0)\). 
After half an oscillation, when \(\alpha = \pi\), the orbit will land on the
negative \(q_u\)-axis with pseudo-radius 
\(u = \hat{\mu}(\pi,\mu_0) \approx \mu_0 + I\hat{\mu}_1(\pi,\mu_0)\).
Hence, the change in pseudo-radius is 
\(u - \mu_0 \approx I\hat{\mu}_1(\pi,\mu_0)\).
If the orbit remains in \(\mathcal{O}\) for the full oscillation, 
it will land on the positive \(q_u\)-axis
with pseudo-radius
\(\tilde{u} \approx \mu_0 + I\hat{\mu}_1(2\pi,\mu_0)\).

Notice that \(b(\alpha,\mu_0)\) is even and 
\(\pi\)-periodic in \(\alpha\), so that
\begin{equation}\label{eqn:bhat-integral-properties}
    \int \limits_{-\pi}^\pi b(\sigma,\mu_0) d\sigma
    = \int \limits_0 ^ {2 \pi} b(\sigma,\mu_0) d\sigma
    = 2 \int \limits_0^\pi b(\sigma,\mu_0) d\sigma
    .
\end{equation}
This implies that 
\(\hat{\mu}_1(2\pi,\mu_0) = 2 \hat{\mu}_1(\pi,\mu_0)\),
which means the change in pseudo-radius after a full oscillation is 
\(\tilde{u} - \mu_0 \approx 2I\hat{\mu}_1(\pi,\mu_0)\).
If \(\hat{\mu}_1(\pi,\mu_0) > 0\), 
then both \(u - \mu_0 > 0\) and \(\tilde{u} - \mu_0 > 0\).
In other words, we can study the average behaviour of \(\hat{\mu}\) by examining
the behaviour at each half oscillation.

We define the Poincar\'{e} section 
\(P_\mathcal{O}(\mu_0) := \hat{\mu}(\pi,\mu_0)\)
corresponding to the change in \(\hat{\mu}\) after half an oscillation.
The section expands into
\[
    P_\mathcal{O}(\mu_0) = \mu_0 + I \hat{\mu}_1(\pi,\mu_0) + R(\pi,\mu_0,I)
    .
\]
Let us define
\[
    Q(\mu_0) := \int \limits_0^\pi b(\sigma,\mu_0)d\sigma
    ,
\]
so that \(\hat{\mu}_1(\pi,\mu_0) = K Q(\mu_0)\).
Note that \(K\) is a positive constant which contains the acrobot's physical
parameters, while \(b(\alpha,\mu)\) is adimensional. 
This means \(Q(\mu_0)\) is identical for every acrobot.
If \(Q(\mu_0)\) is strictly positive, then \(\hat{\mu}_1(\pi,\mu_0)\) will be
positive no matter the values of \(m\), \(g\), \(l\), or \(\bar{q}_a\).

@@

Let \(x(0) \in \mathcal{O}_\epsilon \subset \mathcal{O}\).
Since \(\dot{\alpha} > 0\), the orbit \(x(t)\) spirals clockwise around
the origin.
If this orbit remains in \(\mathcal{O}\), it must intersect
the \(q_u\) axis at some radius \(\mu = \delta\)
which depends on the initial condition \(x(0)\).
Take 
\[
    \underbar{\delta} = 
    \min\limits_{x(0) \in \bar{\mathcal{O}}_\epsilon} \delta(x(0))
    ,
\] 
which exists because \(\bar{\mathcal{O}}_\epsilon\) is compact.
Fruthermore, \(\underbar{\delta} \leq \epsilon\).
From the previous perturbation analysis,
there exists \(I^\prime(\underbar{\delta})\) small enough that
\(P_\mathcal{O}(\mu_0)\) is positive for all 
\(\mu_0 \in [\underbar{\delta},\pi[\).

Suppose \(x(0) \in \mathcal{O}_\epsilon\), and the orbit
intersects the \(q_u\)-axis at some point \(x(t_0) = (u_0, 0)\).
The Poincar\'{e} section \(P_\mathcal{O}(|u_0|)\) is positive because 
\(|u_0| \geq \underbar{\delta}\).
As the acrobot continues its oscillation, it will intersect the \(q_u\) axis
again at a new point \(x(t_1) = (u_1,0)\).
